---
title: "Graphical Representations"
date: "September 12, 2017"
output: html_document
---


```{r include=FALSE}
library(alr4)
library(ggplot2)
library(dplyr)
```

# Scatterplots

## Inheritance of Height

```{r}
dim(Heights)
names(Heights)
head(Heights)
```




## Heights for Mothers and Daughters

```{r}
plot(dheight~mheight,data=Heights)
```

## Heights for Mothers and Daughters

Alternative ways to obtain the scatterplot:

```{r}
plot(dheight~mheight,data=Heights)
qplot(x=mheight, y=dheight, data=Heights) #ggplot2 package
ggplot(data=Heights, aes(x=mheight, y=dheight)) + geom_point() #ggplot2 package
```


## Heights, Variability

```{r}
Heights$mheight_grp <- round(Heights$mheight/2)*2
qplot(data=Heights, x=mheight_grp, y=dheight)
qplot(data=Heights, x=mheight_grp, y=dheight, geom='jitter')
qplot(data=Heights, x=mheight_grp, y=dheight, geom='jitter', color=mheight)
ggplot(data=Heights, aes(x=mheight_grp, y=dheight)) + geom_jitter(aes( color=mheight_grp), alpha=0.5)
```

```{r}
Heights_summ <- Heights %>% group_by(mheight_grp) %>% 
  summarize(sd = sd(dheight), mean=mean(dheight)) #dplyr package
ggplot() + 
  geom_jitter(data=Heights, aes(x=mheight_grp, y=dheight, color=mheight), alpha=0.5) + 
  geom_point(data=Heights_summ, aes(x=mheight_grp, y=mean), color='red',size=2) 
ggplot() + 
  geom_jitter(data=Heights, aes(x=mheight_grp, y=dheight, color=mheight), alpha=0.5) + 
  geom_point(data=Heights_summ, aes(x=mheight_grp, y=mean), color='red',size=2) +
  geom_linerange(data=Heights_summ, aes(x=mheight_grp, ymin=mean-1*sd, ymax=mean+1*sd), color='red')
```

```{r}
help(geom_smooth)
ggplot(data=Heights, aes(x=mheight, y=dheight)) + geom_point() + geom_smooth(method='loess') 
ggplot(data=Heights, aes(x=mheight, y=dheight)) + geom_point() + geom_smooth(method='loess') + geom_smooth(method='lm', color='red') 
```


## Groupwork


### Length versus age for smallmouth bass
1. Why does it make sense to look at length as the response variable and age as the predictor variable?
2. Make a plot with age on the x-axis and length on the y-axis.
3. Add a loess smoother and linear regression line. 

```{r}
head(wblake)
help(wblake)
```


### Predicting Snowfall
1. Make a scatter plot and add a smoother to investigate the relationship between early and late snowfalls in Fort Collins.
2. Color the points by year.  Do you see any trends?

```{r}
head(ftcollinssnow)
help("ftcollinssnow")
```



## Mean Functions

- We are interested on how the distribution of Y changes as X varies
- The mean function focuses on the mean of this distribution:
  - $E(Y|X=x)=$ a function that depends on the value of $x$ such as
  \[E(dheigth|mheight=x)=\beta_0+\beta_1 x\]

## Variance Functions
 - Another characteristic of the distribution of Y is the variance function
 - $Var(Y|X=x)=\sigma^2$

## Summary Graph 

- Anscombe 1973
- Four different data set
- All provide the same slope, intercept, and other summary statistics

## Anscombe Data sets

```{r}
anscombe
```

## Anscombe Data sets

```{r}
options(digits=3)
apply(X = anscombe, MARGIN = 2, mean)
apply(X = anscombe, MARGIN = 2, sd)
xs <- anscombe[,1:4]
ys <- anscombe[,5:8]
for (i in 1:4){
  coefs_i <- coef(lm(ys[,i] ~ xs[,i]))
  print(coefs_i)
}
```

## Summary Graph
```{r}
for (i in 1:4){
  dat <- data.frame(x=xs[,i], y=ys[,i])
  print(ggplot(dat, aes(x=x, y=y)) + geom_point() + geom_smooth(method='lm'))
}
```

