---
title: "Linear Regression"
date: "September 14, 2017"
output: html_document
---


```{r include=FALSE}
library(alr4)
library(ggplot2)
library(dplyr)
```

## Toluca Company

This data set contains information on lot size and work hours for the Toluca company.  The company wishes to study the relationship between lot size (X) and work hours (Y).

```{r}
toluca <- read.table('Data Sets/Chapter  1 Data Sets/tolucadata.txt')
names(toluca) <- c('lotsize', 'workhrs')
x <- toluca$lotsize
y <- toluca$workhrs
```


Make a scatterplot of the data.

```{r}
ggplot(data=toluca, aes(x=lotsize, y=workhrs)) + geom_point()
```


Find the linear regression coefficient estimates.

```{r}
(beta1 <- sum((x-mean(x))*(y-mean(y)))/sum((x-mean(x))^2))
(beta0 <- mean(y)-beta1*mean(x))
```


Add the fitted regression line to the scatterplot.

```{r}
ggplot(data=toluca, aes(x=lotsize, y=workhrs)) + geom_point() + geom_abline(intercept = beta0, slope=beta1, color='red') 
```

Check your work using `geom_smooth` with `method='lm'`.

```{r}
ggplot(data=toluca, aes(x=lotsize, y=workhrs)) + geom_point() + geom_abline(intercept = beta0, slope=beta1, color='red') + geom_smooth(method='lm')
```


Compute the fitted values (estimated mean response) and plot.

```{r}
yhat <- beta0 + beta1*x
toluca$workhrs_pred <- yhat
ggplot(data=toluca, aes(x=lotsize, y=workhrs)) + geom_point() + geom_abline(intercept = beta0, slope=beta1, color='red') + geom_point(aes(y=workhrs_pred), color='red')
```



Compute the residuals.

```{r}
e <- y - yhat
```


Examine the assumptions of the Gauss-Markov Theorem:
1. residuals have mean zero for all values of $x$
2. residuals are homoscedastic (constant variance for all values of $x$)
3. uncorrelated errors (based on sampling design)

```{r}
toluca$residual <- e
ggplot(toluca, aes(x=lotsize, y=residual)) + geom_point() + geom_hline(yintercept=0, linetype=2)
```

The plot does not show any notable evidence of non-constant mean or non-constant variance (heteroskedasticity).


Estimate the residual variance and plot as a band around fitted regression line.

```{r}
n <- nrow(toluca)
sigma_sq <- sum(e^2)/(n-2)
sigma <- sqrt(sigma_sq)
ggplot(data=toluca, aes(x=lotsize, y=workhrs)) + geom_point() + geom_abline(intercept = beta0, slope=beta1, color='red') + geom_ribbon(aes(ymin=workhrs_pred-2*sigma, ymax=workhrs_pred+2*sigma), alpha=0.5)
```


The `lm()` function can be used to perform linear regression automatically:

```{r}
model <- lm(workhrs ~ lotsize, data=toluca)
summary(model)
```

