---
title: "Graphical Representations"
date: "September 12, 2017"
output: html_document
---

```{r, results = 'hide'}
rm(list = ls())
getwd()
setwd("~/GitHub/PopGen/linear_models")
```


```{r include=FALSE}
library(alr4)
library(ggplot2)
library(dplyr)
```

## Inheritance of Height

```{r}
ggplot(data=Heights, aes(x=mheight, y=dheight)) + geom_point() #ggplot2 package
```


## Toluca Company

This data set contains information on lot size and work hours for the Toluca company.  The company wishes to study the relationship between lot size (X) and work hours (Y).

```{r}
toluca <- read.table('data/Chapter_1_Data_Sets/tolucadata.txt')
names(toluca) <- c('lotsize', 'workhrs')
x <- toluca$lotsize
y <- toluca$workhrs
```


Make a scatterplot of the data.

```{r}
ggplot(data=toluca, aes(x=lotsize, y=workhrs)) + geom_point() #ggplot2 package
```


Find the linear regression coefficient estimates.

```{r}
(beta1 <- sum((x-mean(x))*(y-mean(y)))/sum((x-mean(x))^2))
(beta0 <- mean(y)- (beta1*mean(x)))
```


Add the fitted regression line to the scatterplot.

```{r}
y_hat <- beta0 + (beta1 * x)
ggplot(data=toluca, aes(x=lotsize, y=workhrs)) + geom_point() + #ggplot2 package
  geom_line(color='blue', aes(x, y_hat))
```


Compute the residuals.

```{r}
eps <- y - y_hat
```


Examine the assumptions of the Gauss-Markov Theorem.

```{r}
mean(eps)
sd(eps)
```




