---
title: "Linear Regression"
date: "September 14, 2017"
output: html_document
---

```{r, results = 'hide'}
rm(list = ls())
getwd()
setwd("~/GitHub/PopGen/linear_models")
```

```{r include=FALSE}
library(alr4)
library(ggplot2)
library(dplyr)
```

## Toluca Company

This data set contains information on lot size and work hours for the Toluca company.  The company wishes to study the relationship between lot size (X) and work hours (Y).

```{r}
toluca <- read.table('data/Chapter_1_Data_Sets/tolucadata.txt')
names(toluca) <- c('lotsize', 'workhrs')
x <- toluca$lotsize
y <- toluca$workhrs
```


Make a scatterplot of the data.

```{r}
ggplot(data=toluca, aes(x=lotsize, y=workhrs)) + geom_point()
```


Find the linear regression coefficient estimates.

```{r}
(beta1 <- sum((x-mean(x))*(y-mean(y)))/sum((x-mean(x))^2))
(beta0 <- mean(y)-beta1*mean(x))
```


Add the fitted regression line to the scatterplot.

```{r}
ggplot(data=toluca, aes(x=lotsize, y=workhrs)) + geom_point() + geom_abline(intercept = beta0, slope=beta1, color='red') 
```

Check your work using `geom_smooth` with `method='lm'`.

```{r}
ggplot(data=toluca, aes(x=lotsize, y=workhrs)) + geom_point() + geom_abline(intercept = beta0, slope=beta1, color='red') + geom_smooth(method='lm')
```


Compute the fitted values (estimated mean response).

```{r}
y_hat <- beta0 + (beta1 * x)
ggplot(data=toluca, aes(x=lotsize, y=workhrs)) + geom_point() + #ggplot2 package
  geom_line(color='red', aes(x, y_hat))
```



Compute the residuals.

```{r}
eps <- y - y_hat
```


Examine the assumptions of the Gauss-Markov Theorem:
1. residuals have mean zero (always true in OLS)
2. residuals are homoscedastic
3. uncorrelated errors (based on sampling design)

```{r}
mean(eps)
sd(eps)
```



Estimate the residual variance and plot as a band around fitted regression line.

```{r}
n <- nrow(toluca)
ggplot()
```


