---
title: "Groupwork 9/12"
author: "Your Name Here"
output: html_document
---


```{r include=FALSE}
#install.packages("alr4") <- run this if you have never installed the alr4 package
library(alr4)
library(ggplot2)
library(dplyr)
```

```{r}
head(wblake)
help(wblake)
```

### Length versus age for smallmouth bass
1. Using `ggplot` or `qplot`, make a plot with age on the x-axis and length on the y-axis using the "point" geom.
2. Avoid overplotting by using the "jitter" geom, with or without transparency.  To avoid over-jittering, set `width=0.1` and `height=0`.
3. Describe the relationship between Age and Length.  
3. Color the points by Scale.  Use `scale_color_gradientn()` to create a color scale with at least 4 colors.  
4. Describe the relationship between Scale and Age.
5. Conditional on Age, describe the relationship between Scale and Length.

1.

```{r}
ggplot(data=wblake, aes(x=Age, y=Length)) + geom_point()
```

2. 
```{r}
ggplot(data=wblake, aes(x=Age, y=Length)) + geom_jitter(alpha=0.5, width=0.1, height=0)
```

3. 
```{r}
ggplot(data=wblake, aes(x=Age, y=Length)) + 
  #geom_jitter(alpha=0.5, width=0.1, height=0) +
  geom_point(aes(colour = Scale)) +
  scale_colour_gradientn(colours = terrain.colors(10))
```