---
title: 'I519: Homework 1'
author: "Will Shoemaker"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
geometry: margin=2.54cm
---

## Overview


## Set working directory
```{r}
rm(list=ls()) 
getwd() 
setwd("~/github/PopGen/I519/HW1/") 
```

## Import packages
```{r}
library("quantmod")
library("ggplot2")
library("reshape2")
library("wesanderson")
library(data.table)

```

## Import the data and add headers
```{r}
draft <- read.table("./genesize-draft.txt",header=F) 
complete <- read.table("./genesize-complete.txt",header=T) 

colnames(draft) <- c("Strain", "Genes")
colnames(complete) <- c("Strain", "Genes")

```

# Mean gene number
```{r}
mean(draft[,2])
mean(complete[,2])
```

So the draft genomes have a mean gene number of ~2,679 and the complete genomes have a mean gene number of ~2522. Let's look if there's a significant difference. 

## Examine the quantile-quantile plots for the samples
First we make a Q-Q plot that examines both samples.

```{r}
qqplot(draft[,2], complete[,2])

xlim = range(1800, draft)
ylim = range(1800, complete)

qqplot(draft[,2], complete[,2],
xlim = ylim, ylim = ylim,
xlab = "Draft Genomes",
ylab = "Complete Genomes",
main = "Gene Number")
abline(a=0, b=1, lty="dotted")
```

Then we make a Q-Q plot for each sample that compares the theoretical quantiles with sample quantiles.

```{r}
qqnorm(draft[,2],
main = "Gene number in draft genomes")
qqline(draft[,2])
qqnorm(complete[,2],
main = "Gene number in complete genomes")
qqline(complete[,2])
```

We see from above that there is a clear deviation from the theoretical expectation for each sample, suggesting that it would not be a good idea to assume normality. We can then proceed with a Wilcoxon rank-sum test.

```{r}
wilcox.test(draft[,2], complete[,2], alternative = c("two.sided"), paired = FALSE, conf.level = 0.95)
```

There is a significant difference in the number of genes between draft and complete genomes. 

```{r}
draft$Type <- rep("Draft",nrow(draft)) 
complete$Type <- rep("Complete",nrow(complete)) 
mergeData <- rbind(draft, complete)
mergeData$logGenes <- log(mergeData[,2])
class(mergeData)
head(mergeData)
```



```{r}
palette <- wes_palette(5, name = "FantasticFox", type = "discrete") 
ggplot(mergeData, aes(x=Type, y=Genes, fill = Type)) +
  geom_violin(trim=FALSE) + 
  geom_boxplot(width=0.1) + 
  scale_fill_manual(values=palette[-2]) + 
  xlab("Genome Type") + 
  scale_size_area("Genome Type") + 
  ylab("Gene Number") + 
  guides(fill=guide_legend(title=NULL))
```
